---
title: "Final Project: Neural Code"
author: "Apurv Srivastav"
date: "11/11/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message= FALSE, warning = FALSE)
```


```{r}
library(kableExtra)
library(IRdisplay)
library(dplyr)
library(tidyverse)
library(ggpubr)
library(rstatix)
library(ggplot2)
library(nlme)
library(geepack)
library(gridExtra)
```

##### $\bf \text{ Data downloaded:}$

```{r cars}
ID=22;
#dat.path='./Data/NMA/' # Replace with your wd
dat.path='C:/Users/ssrivas/Desktop/Apurv/UC Davis/MS Degree/MS comprehensive/NMA' # Replace with your wd
#dat = readRDS(paste(dat.path,"session",ID,".rds",sep=''))
dat = readRDS('session22.rds')
names(dat)

# Summarize the active trials

scenario.type=c('L (1, ip)','R (-1, ct)','N (0)','B')
contrast_LmR = dat$contrast_left-dat$contrast_right;
scenario = numeric(length(contrast_LmR))
for(i in 1:length(scenario)){
  if( dat$contrast_left[i]==0 &  dat$contrast_right[i]==0){
    scenario[i]='N (0)'
  }else if (contrast_LmR[i] >0){
    scenario[i]='L (1, ip)'
  }else if (contrast_LmR[i] < 0){
    scenario[i]='R (-1, ct)'
  }else{
    scenario[i]='B'
  }
  
}
dat$scenario=scenario;


sum.tab<-matrix(0,nrow=length(scenario.type),ncol=7)
for(i in 1:length(scenario.type) ){
  ids = which(dat$scenario==scenario.type[i])
  
  n.tmp=length(ids);
  fb=dat$feedback_type[ids]
  rsp=dat$response[ids]
  cts=dat$contrast_left[ids]-dat$contrast_right[ids]
  if(i==4){
    # success: not 0
    success= (rsp!=0);
    
  }else if (i==3){
    # success:  0
    success= (rsp==0);
  }else{
    # success: same sign
    success = (rsp*cts)>0
  }
  
  tmp<-c(sum(success==FALSE),
         sum(success==TRUE & fb==1),
         sum(success==TRUE & fb==-1),
         n.tmp)
  sum.tab[i,]<-c(tmp,tmp[1:3]/tmp[4])
}


rownames(sum.tab)<-scenario.type
colnames(sum.tab)<-c('Failure', 'Success', 'Success w/o rewards', 'Total','Failure (prob)', 'Success (prob)', 'Success w/o rewards  (prob)' )

round(sum.tab,digits=2) %>%
  kable("html",caption=paste("Summary of stimuli scenarios and response across", length(dat$feedback_type ) ,"trials for Session", ID, "Mouse", 
                             dat$mouse_name, "Date", dat$date_exp )) # %>%
  #as.character() %>%
  #display_html()
```


```{r}
class(dat)
str(dat)
table(scenario)
table(scenario.type)
sum.tab
#table(brain_region)

#dim(dat)
#head(dat)
```
```{r}
spks<-dat$spks
class(spks)

data1<-data.frame(spks[, ,51:90])
brain_region<-dat$brain_region
brain_data.Q1<-data.frame(cbind(brain_region,data1))
#data1$brain_data<-rep(dat$brain_region,250)

#dim(data1)
dim(brain_data.Q1)
class(brain_data.Q1)
#head(brain_data)
table(brain_region)
```


##### agrregate data for brain_data.Q1: mean 

```{r, warning=FALSE, echo=FALSE}
outlier_brain_data.Q1<-data.frame(brain_data.Q1)
#dim(outlier_brain_data.Q1)
#class(brain_data.Q1)
#head(brain_data.Q1)
attach(outlier_brain_data.Q1)
outlier_agg.Q1 = aggregate(outlier_brain_data.Q1[,-1],
               by = list(as.factor(outlier_brain_data.Q1$brain_region)),FUN = mean)
```


```{r}
#dim(outlier_agg.Q1)
str(outlier_agg.Q1)
```


```{r}
noutlier_agg.Q1<-data.frame(t(outlier_agg.Q1[,-1]))
names(noutlier_agg.Q1)<-c("basal.ganglia","midbrain","other","other.ctx", "vis.ctx")
#dim(noutlier_agg.Q1)
head(noutlier_agg.Q1)
#class(noutlier_agg.Q1)
```

```{r}
# Compute t-test
res1 <- t.test(noutlier_agg.Q1$other, noutlier_agg.Q1$basal.ganglia, paired = TRUE)
res2 <- t.test(noutlier_agg.Q1$other, noutlier_agg.Q1$midbrain, paired = TRUE)
res3 <- t.test(noutlier_agg.Q1$other, noutlier_agg.Q1$other.ctx, paired = TRUE)
res4 <- t.test(noutlier_agg.Q1$other, noutlier_agg.Q1$vis.ctx, paired = TRUE)
res1;res2;res3;res4
```





```{r}
nbrain_data.Q1 <- brain_data.Q1 %>%                               # Replacing values
  mutate(brain_region = replace(brain_region, brain_region == "other", "other ctx"))
#data_new

table(nbrain_data.Q1$brain_region)
```

```{r}
data.Q1<-t(nbrain_data.Q1[,-1])
#dim(data.Q1)
```

```{r}
spks<-dat$spks
class(spks)

data2<-data.frame(spks[, ,31:90])
#brain_region<-dat$brain_region
brain_data.Q2<-data.frame(cbind(brain_region,data2))
#data1$brain_data<-rep(dat$brain_region,250)

#dim(data1)
#dim(brain_data.Q2)
class(brain_data.Q2)
#head(brain_data)
#table(brain_region)
```



```{r}
nbrain_data.Q2 <- brain_data.Q2 %>%                               # Replacing values
  mutate(brain_region = replace(brain_region, brain_region == "other", "other ctx"))
#data_new

table(nbrain_data.Q2$brain_region)
```

```{r}
data.Q2<-t(nbrain_data.Q2[,-1])
#dim(data.Q2)
```

```{r}
#write.table(t(brain_data.Q1), file="brain_data.Q1.txt")
#write.table(t(brain_data.Q2), file="brain_data.Q2.txt")
```



```{r}
#head(ndata2)
time.bin<-rep(51:90, each=444)
trial.no<-rep(1:444, each=40)
contrast_right<-dat$contrast_right
contrast_left<-dat$contrast_left
stimulus<-contrast_left-contrast_right
stimulus.type<-rep(stimulus,40)


bin_size<-rep(dat$bin_size,40)
feedback_type<-rep(dat$feedback_type,40)
stim_onset<-rep(dat$stim_onset,40)
reaction_time<- rep(dat$reaction_time[,1], 40)
reaction_type<- rep(dat$reaction_time[,2], 40)
#names(reaction_time)<-c("reaction_time","reaction_type")
response<-rep(dat$response,40)
scenario<-rep(dat$scenario, 40)

ndata.Q1<-data.frame(cbind(trial.no,time.bin, stimulus.type, bin_size, feedback_type,stim_onset,response,scenario,reaction_time,reaction_type,contrast_right, contrast_left))
#names(ndata.Q1)<-c("trial.no", "time.bin", "stimulus.type", c("V1":"V646"))

#dim(ndata.Q1)
str(ndata.Q1)
#head(ndata.Q1)
#tail(ndata.Q1)
```


```{r}
time.bin<-rep(31:90, each=444)
trial.no<-rep(1:444, each=60)
contrast_right<-dat$contrast_right
contrast_left<-dat$contrast_left
stimulus<-contrast_left-contrast_right
stimulus.type<-rep(stimulus,60)


bin_size<-rep(dat$bin_size,60)
feedback_type<-rep(dat$feedback_type,60)
stim_onset<-rep(dat$stim_onset,60)
reaction_time<- rep(dat$reaction_time[,1], 60)
reaction_type<- rep(dat$reaction_time[,2], 60)
#names(reaction_time)<-c("reaction_time","reaction_type")
response<-rep(dat$response,60)
scenario<-rep(dat$scenario, 60)

ndata.Q2<-data.frame(cbind(trial.no,time.bin, stimulus.type, bin_size, feedback_type,stim_onset,response,scenario,reaction_time,reaction_type,contrast_right, contrast_left))

#names(ndata.Q2)<-c("trial.no", "time.bin", "stimulus.type", c("V1":"V646"))
dim(ndata.Q2)
str(ndata.Q2)
```


```{r}
#ndata..Q1$spks<-as.integer(ndata..Q1$spks)
ndata.Q1$bin_size<-as.numeric(ndata.Q1$bin_size)
ndata.Q1$feedback_type<-as.factor(ndata.Q1$feedback_type)
ndata.Q1$stim_onset<-as.numeric(ndata.Q1$stim_onset)
ndata.Q1$contrast_right<-as.numeric(ndata.Q1$contrast_right)
ndata.Q1$contrast_left<-as.numeric(ndata.Q1$contrast_left)
ndata.Q1$stimulus.type<-as.factor(ndata.Q1$stimulus.type)
#neuro_data$brain_region<-as.factor(data$brain_region)
ndata.Q1$response<-as.numeric(ndata.Q1$response)
ndata.Q1$reaction_time<-as.numeric(ndata.Q1$reaction_time)
ndata.Q1$reaction_type<-as.factor(ndata.Q1$reaction_type)
ndata.Q1$scenario<-as.factor(ndata.Q1$scenario)

ndata.Q1$trial.no<-as.factor(ndata.Q1$trial.no)
ndata.Q1$time.bin<-as.factor(ndata.Q1$time.bin)

attach(ndata.Q1)

dim(ndata.Q1)
str(ndata.Q1)
```



```{r}
#ndata..Q1$spks<-as.integer(ndata..Q1$spks)
ndata.Q2$bin_size<-as.numeric(ndata.Q2$bin_size)
ndata.Q2$feedback_type<-as.factor(ndata.Q2$feedback_type)
ndata.Q2$stim_onset<-as.numeric(ndata.Q2$stim_onset)
ndata.Q2$contrast_right<-as.numeric(ndata.Q2$contrast_right)
ndata.Q2$contrast_left<-as.numeric(ndata.Q2$contrast_left)
ndata.Q2$stimulus.type<-as.factor(ndata.Q2$stimulus.type)
#neuro_data$brain_region<-as.factor(data$brain_region)
ndata.Q2$response<-as.numeric(ndata.Q2$response)
ndata.Q2$reaction_time<-as.numeric(ndata.Q2$reaction_time)
ndata.Q2$reaction_type<-as.factor(ndata.Q2$reaction_type)
ndata.Q2$scenario<-as.factor(ndata.Q2$scenario)

ndata.Q2$trial.no<-as.factor(ndata.Q2$trial.no)
ndata.Q2$time.bin<-as.factor(ndata.Q2$time.bin)

attach(ndata.Q2)

dim(ndata.Q2)
str(ndata.Q2)
```


```{r}

#write.table(ndata3, file="neuro_data.txt")
#write.table(t(data.frame(brain_data)), file="nbrain_data.txt")
```

```{r}
table(nbrain_data.Q1$brain_region)
```


##### agrregate data for Q1: mean 

```{r}

nbrain_data.Q1<-data.frame(nbrain_data.Q1)
#dim(nbrain_data.Q1)
#class(brain_data.Q1)
#head(brain_data.Q1)
attach(nbrain_data.Q1)
agg.Q1 = aggregate(nbrain_data.Q1[,-1],
               by = list(as.factor(nbrain_data.Q1$brain_region)),FUN = mean)
```


```{r}
#print(agg.Q1)
dim(agg.Q1)
#head(agg.Q1)
#class(agg.Q1)

```


```{r}
#summary(t(agg.Q1))
```

##### agrregate data for Q2: mean 

```{r}
nbrain_data.Q2<-data.frame(nbrain_data.Q2)
#dim(nbrain_data.Q2)
#class(brain_data.Q1)
#head(brain_data.Q1)
attach(nbrain_data.Q2)
agg.Q2 = aggregate(nbrain_data.Q2[,-1],
               by = list(as.factor(nbrain_data.Q2$brain_region)),FUN = mean)
```


```{r}
dim(agg.Q2)
#head(agg.Q2)
#class(agg.Q2)

```

##### Complete data for Q1

```{r}
complete_data.Q1<-cbind(ndata.Q1[,1:12],t(agg.Q1[,-1]))

names(complete_data.Q1)<-c("trial.no","time.bin","stimulus.type","bin_size","feedback_type","stim_onset","response","scenario", "reaction_time", "reaction_type", "contrast_right","contrast_left", "basal.ganglia","midbrain","other.ctx", "vis.ctx")
dim(complete_data.Q1)
str(complete_data.Q1)
```

##### Complete data for Q2

```{r}
complete_data.Q2<-cbind(ndata.Q2[,1:12],t(agg.Q2[,-1]))

names(complete_data.Q2)<-c("trial.no","time.bin","stimulus.type","bin_size","feedback_type","stim_onset","response","scenario", "reaction_time", "reaction_type", "contrast_right","contrast_left", "basal.ganglia","midbrain","other.ctx", "vis.ctx")
dim(complete_data.Q2)
str(complete_data.Q2)
```


```{r}
#write.table(complete_data.Q1, file="complete_brain_data_Q1.txt")
#write.table(complete_data.Q2, file="complete_brain_data_Q2.txt")
```

##### $\bf \text{Summary data for Question 1:}$

```{r}
summdata.Q1 = group_by(complete_data.Q1, time.bin, stimulus.type) %>%
  summarise(
    
    time.bin = time.bin,
    #trial.no = trial.no,
    stimulus.type=stimulus.type,
    mean_basal.ganglia = mean(basal.ganglia),
    mean_midbrain=mean(midbrain),
    mean_other.ctx=mean(other.ctx), 
    mean_vis.ctx=mean(vis.ctx)
  )
summdata.Q1<-data.frame(unique(summdata.Q1))


summdata.Q1[1:9,]

dim(summdata.Q1)
#print(summ_table.Q1)
```


```{r}

### Another method to calculate summary
#summdata.Q1 %>%
 # group_by(stimulus.type, time.bin) %>%
#  get_summary_stats(mean_basal.ganglia, type = "mean_sd")
```


##### $\bf \text{Visualization for Question 1:}$ 

```{r}

bxp.Q1b1 <- ggboxplot(
  summdata.Q1, x = "stimulus.type", y = "mean_basal.ganglia",
  color = "stimulus.type", add = "point"
  )
#bxp.Q1b


bxp.Q1b2 <- ggboxplot(
  summdata.Q1, x = "stimulus.type", y = "mean_midbrain",
  color = "stimulus.type", add = "point"
  )
#bxp.Q1b2

bxp.Q1b3 <- ggboxplot(
  summdata.Q1, x = "stimulus.type", y = "mean_vis.ctx",
  color = "stimulus.type", add = "point"
  )
#bxp.Q1b3

bxp.Q1b4 <- ggboxplot(
  summdata.Q1, x = "stimulus.type", y = "mean_other.ctx",
  color = "stimulus.type", add = "point"
  )
#bxp.Q1b4


#############################################################################################
##### time bin boxplots

bxp.Q1c1 <- ggboxplot(summdata.Q1, x = "time.bin", y = "mean_basal.ganglia", add = "point")
#bxp.Q1c

bxp.Q1c2 <- ggboxplot(summdata.Q1, x = "time.bin", y = "mean_midbrain", add = "point")
#bxp.Q1c2

bxp.Q1c3 <- ggboxplot(summdata.Q1, x = "time.bin", y = "mean_vis.ctx", add = "point")
#bxp.Q1c3

bxp.Q1c4 <- ggboxplot(summdata.Q1, x = "time.bin", y = "mean_other.ctx", add = "point")
#bxp.Q1c4



###########################################################################################
##### time bin plots with points

bxp.Q1a1 <- ggboxplot(
  summdata.Q1, x = "time.bin", y = "mean_basal.ganglia", color = "stimulus.type", add = "point") 
#palette = "jco")
#bxp.Q1a1

bxp.Q1a2 <- ggboxplot(
  summdata.Q1, x = "time.bin", y = "mean_midbrain", color = "stimulus.type", add = "point") 
#palette = "jco")
#bxp.Q1a2


bxp.Q1a3 <- ggboxplot(
  summdata.Q1, x = "time.bin", y = "mean_vis.ctx", color = "stimulus.type", add = "point") 
#palette = "jco")
#bxp.Q1a3


bxp.Q1a4 <- ggboxplot(
  summdata.Q1, x = "time.bin", y = "mean_other.ctx", color = "stimulus.type", add = "point") 
#palette = "jco")
#bxp.Q1a4


```



```{r}
#grid.arrange(bxp.Q1b,bxp.Q1b2,bxp.Q1b3,bxp.Q1b4, ncol=2)
grid.arrange(bxp.Q1c1,bxp.Q1c2,bxp.Q1c3,bxp.Q1c4, ncol=2)

grid.arrange(bxp.Q1b1,bxp.Q1b2, nrow=2)
grid.arrange(bxp.Q1b3,bxp.Q1b4, nrow=2)
```


##### $\bf \text{Check assumptions: Outliers}$

```{r}
summdata.Q1 %>%
  group_by(time.bin) %>%
  identify_outliers(mean_basal.ganglia)

summdata.Q1 %>%
  group_by(stimulus.type) %>%
  identify_outliers(mean_midbrain)

summdata.Q1 %>%
  group_by(time.bin) %>%
  identify_outliers(mean_other.ctx)

summdata.Q1 %>%
  group_by(time.bin) %>%
  identify_outliers(mean_vis.ctx)

```

##### $\bf Comments:$ There were no extreme outliers for stimulus.type

\ \

##### $\bf \text{Normality assumption:}$

```{r}
summdata.Q1 %>%
  group_by(stimulus.type) %>%
  shapiro_test(mean_basal.ganglia)

summdata.Q1 %>%
  group_by(stimulus.type) %>%
  shapiro_test(mean_midbrain)

summdata.Q1 %>%
  group_by(stimulus.type) %>%
  shapiro_test(mean_vis.ctx)

summdata.Q1 %>%
  group_by(stimulus.type) %>%
  shapiro_test(mean_other.ctx)
```

##### $\bf Comments:$ The mean_basal.ganglia score was normally distributed at each time point, as assessed by Shapiro-Wilk’s test (p > 0.05).

##### The normality assumption can be checked by computing Shapiro-Wilk test for each stimulus point. If the data is normally distributed, the p-value should be greater than 0.05.

##### Note that, if your sample size is greater than 50, the normal QQ plot is preferred because at larger sample sizes the Shapiro-Wilk test becomes very sensitive even to a minor deviation from normality.


\ \

##### $\bf QQ-Plots:$

```{r}
ggqqplot(summdata.Q1, "mean_basal.ganglia", facet.by = "stimulus.type",main="QQ plots for Basal Ganglia across Stimulus Type")

ggqqplot(summdata.Q1, "mean_midbrain", facet.by = "stimulus.type",main="QQ plots for Midbrain across Stimulus Type")

ggqqplot(summdata.Q1, "mean_vis.ctx", facet.by = "stimulus.type",main="QQ plots for Visual Cortexacross Stimulus Type")

ggqqplot(summdata.Q1, "mean_other.ctx", facet.by = "stimulus.type",main="QQ plots for Other Cortex across Stimulus Type")
```

##### $\bf Comments:$ From the plot above, as all the points fall approximately along the reference line, we can assume normality.

 \ \
 
##### $\bf \text{Sphericity Assumption:}$

##### Assumption of sphericity: The assumption of sphericity refers to the equality of variances of the differences between treatment levels. In Repeated Measures ANOVA it is a measure of the homogeneity of the variances of the differences between levels so it is quite similar to homogeneity of variance in between-groups in the univariate ANOVA.

##### The assumption of sphericity will be automatically checked during the computation of the ANOVA test using the R function anova_test() [rstatix package]. The Mauchly’s test is internally used to assess the sphericity assumption.

##### By using the function get_anova_table() [rstatix] to extract the ANOVA table, the Greenhouse-Geisser sphericity correction is automatically applied to factors violating the sphericity assumption.


```{r}
str(summdata.Q1)
```
```{r}
summdata.Q1.BG<-summdata.Q1 %>%
  group_by(stimulus.type) %>%
  get_summary_stats(mean_basal.ganglia, type = "mean_sd")

summdata.Q1.MB<-summdata.Q1 %>%
  group_by(stimulus.type) %>%
  get_summary_stats(mean_midbrain, type = "mean_sd")

summdata.Q1.OC<-summdata.Q1 %>%
  group_by(stimulus.type) %>%
  get_summary_stats(mean_other.ctx, type = "mean_sd")

summdata.Q1.VC<-summdata.Q1 %>%
  group_by(stimulus.type) %>%
  get_summary_stats( mean_vis.ctx, type = "mean_sd")

write.csv(summdata.Q1.BG, file="summdata.Q1.BG.csv")
write.csv(summdata.Q1.MB, file="summdata.Q1.MB.csv")
write.csv(summdata.Q1.OC, file="summdata.Q1.OC.csv")
write.csv(summdata.Q1.VC, file="summdata.Q1.VC.csv")
```


```{r}
res.aov1 <- aov(mean_basal.ganglia~factor(stimulus.type)+Error(factor(time.bin)), data = summdata.Q1)
summary(res.aov1)

res.aov2 <- aov(mean_midbrain~factor(stimulus.type)+Error(factor(time.bin)), data = summdata.Q1)
summary(res.aov2)

res.aov3 <- aov(mean_other.ctx~factor(stimulus.type)+Error(factor(time.bin)), data = summdata.Q1)
summary(res.aov3)

res.aov4 <- aov(mean_vis.ctx~factor(stimulus.type)+Error(factor(time.bin)), data = summdata.Q1)
summary(res.aov4)
```

```{r}
##### Another way to perform one way ANOVA

#model = aov(formula = mean_basal.ganglia ~ factor(stimulus.type)+Error(factor(time.bin)/factor(stimulus.type)), data=summdata.Q1) 
#summary(model)
```

```{r}
res.aov11 <- anova_test(data = summdata.Q1, dv = mean_basal.ganglia, wid = time.bin, within = stimulus.type)
get_anova_table(res.aov11)
#summary(res.aov1)

res.aov22 <- anova_test(data = summdata.Q1, dv = mean_midbrain, wid = time.bin, within = stimulus.type)
get_anova_table(res.aov22)

res.aov33 <- anova_test(data = summdata.Q1, dv = mean_other.ctx, wid =  time.bin, within = stimulus.type)
get_anova_table(res.aov33)

res.aov44 <- anova_test(data = summdata.Q1, dv = mean_vis.ctx, wid =  time.bin, within = stimulus.type)
get_anova_table(res.aov44)

```

##### Results showed that the type of stimulus type used lead to statistically significant differences in mean_basal.ganglia during the time.bin (F(4, 158) = 9.38, p = 6.7e-07).

##### Results showed that the type of stimulus type used lead to statistically significant differences in mean_midbrain during the time.bin (F(5, 209) = 23.3, p=1.81e-19).

##### Results showed that the type of stimulus type used lead to statistically significant differences in mean_other.ctx during the time.bin (F(3, 122) = 39.9, p=1.5e-18).

##### Results showed that the type of stimulus type used lead to statistically significant differences in mean_vis.ctx during the time.bin (F(3, 117) = 9.23, p = 1.6e-05).


########################################################################################################################################### 


##### The mean_basal.ganglia score was statistically significantly different at the different stimulus points, p = 6.7e-07, eta2[g] = 0.163.
##### The mean_midbrain score was statistically significantly different at the different stimulus points, p = 1.81e-19, eta2[g] = 0.25.
##### The mean_other.ctx score was statistically significantly different at the different stimulus points, p = 1.5e-18, eta2[g] = 0.221.
##### The mean_vis.ctx score was statistically significantly different at the different stimulus points, p = 1.6e-05, eta2[g] = 0.105.

##### $\bullet:$ ges is the generalized effect size (amount of variability due to the within-subjects factor) i.e.,  is useful in repeated-measures designs, as it can estimate what a within-subject effect size would have been had that predictor been manipulated between-subjects.


##### $\bf \text{Post-hoc tests:}$

##### multiple pairwise paired t-tests between the levels of the within-subjects factor (here stimulus-type). P-values are adjusted using the Bonferroni multiple testing correction method.

```{r}
# pairwise comparisons
pwc.Q1 <- summdata.Q1 %>%
  pairwise_t_test(
    mean_basal.ganglia ~ stimulus.type, paired = TRUE,
    p.adjust.method = "bonferroni"
    )
pwc.Q1

pwc.Q2 <- summdata.Q1 %>%
  pairwise_t_test(
    mean_midbrain ~ stimulus.type, paired = TRUE,
    p.adjust.method = "bonferroni"
    )
pwc.Q2

pwc.Q3 <- summdata.Q1 %>%
  pairwise_t_test(
    mean_vis.ctx ~ stimulus.type, paired = TRUE,
    p.adjust.method = "bonferroni"
    )
pwc.Q3

pwc.Q4 <- summdata.Q1 %>%
  pairwise_t_test(
    mean_other.ctx ~ stimulus.type, paired = TRUE,
    p.adjust.method = "bonferroni"
    )
pwc.Q4
```


```{r}
table.pwc.Q1<-data.frame(pwc.Q1)
#which(table.pwc.Q4$(p.adj>=0.005)
p.values_BG<-data.frame(subset(table.pwc.Q1, subset=(p.adj<=0.05)))
p.values_BG

table.pwc.Q2<-data.frame(pwc.Q2)
#which(table.pwc.Q4$(p.adj>=0.005)
p.values_MB<-data.frame(subset(table.pwc.Q2, subset=(p.adj<=0.05)))
p.values_MB

table.pwc.Q3<-data.frame(pwc.Q3)
#which(table.pwc.Q4$(p.adj>=0.005)
p.values_VC<- data.frame(subset(table.pwc.Q3, subset=(p.adj<=0.05)))
p.values_VC

table.pwc.Q4<-data.frame(pwc.Q4)
#which(table.pwc.Q4$(p.adj>=0.005)
p.values_OC<-data.frame(subset(table.pwc.Q4, subset=(p.adj<=0.005)))
p.values_OC
      
write.table(p.values_BG, file="p.values_BG.txt")
write.table(p.values_MB, file="p.values_MB.txt")
write.table(p.values_VC, file="p.values_VC.txt")
write.table(p.values_OC, file="p.values_OC.txt")
```
##### Report: The mean_basal.ganglia score was statistically significantly different at the different time points, F(2, 18) = 55.5, p < 0.002, generalized eta squared = 0.16.

##### Post-hoc analyses with a Bonferroni adjustment revealed that the following pairwise differences, between stimulus type, were statistically significantly different (p <= 0.05).

\ \

##### $\bf \text{Visualization: box plots with p-values}$

```{r}
pwc.Q1 <- pwc.Q1 %>% add_xy_position(x = "stimulus.type")
bxp.Q1b1 + 
  stat_pvalue_manual(pwc.Q1) +
  labs(
    subtitle = get_test_label(res.aov11, detailed = TRUE),
    caption = get_pwc_label(pwc.Q1)
  )

pwc.Q2 <- pwc.Q2 %>% add_xy_position(x = "stimulus.type")
bxp.Q1b2 + 
  stat_pvalue_manual(pwc.Q2) +
  labs(
    subtitle = get_test_label(res.aov22, detailed = TRUE),
    caption = get_pwc_label(pwc.Q2)
  )

pwc.Q3 <- pwc.Q3 %>% add_xy_position(x = "stimulus.type")
bxp.Q1b3 + 
  stat_pvalue_manual(pwc.Q3) +
  labs(
    subtitle = get_test_label(res.aov33, detailed = TRUE),
    caption = get_pwc_label(pwc.Q3)
  )

pwc.Q4 <- pwc.Q4 %>% add_xy_position(x = "stimulus.type")
bxp.Q1b4 + 
  stat_pvalue_manual(pwc.Q4) +
  labs(
    subtitle = get_test_label(res.aov44, detailed = TRUE),
    caption = get_pwc_label(pwc.Q4)
  )
```


```{r}
#str(complete_data.Q1)
```

##### $\bf \text{Examine whether there exist heterogeneous effects of stimuli across neurons within each brain regions.}$

```{r}
oneway.BG <- aov(basal.ganglia ~ stimulus.type, data = complete_data.Q1)
summary(oneway.BG)

oneway.MB <- aov(midbrain ~ stimulus.type, data = complete_data.Q1)
summary(oneway.MB)

oneway.OC <- aov(other.ctx ~ stimulus.type, data = complete_data.Q1)
summary(oneway.OC)

oneway.VC <- aov(vis.ctx ~ stimulus.type, data = complete_data.Q1)
summary(oneway.VC)
```

##### The p-value of the stimulus.type variable is quite low so it appears that the type of stimulus.type used has a real impact on the brain region of basal.ganglia.

\ \

##### Wide form to Long form Data for Question 1

```{r}
complete_data.Q1$idvar<-c(1:17760)
library("reshape2") 
data_long.Q1 <- melt(complete_data.Q1[,c(2,3,5,13:16)],                                 # Apply melt function
                  id.vars = c("time.bin", "stimulus.type", "feedback_type"))
#data_long   
names(data_long.Q1)<-c("time.bin","stimulus.type", "feedback_type", "brain_region",  "response")

dim(data_long.Q1)
head(data_long.Q1)
```

\ \

##### $\bf \text{Examine whether each region's response to stimuli is associated with the outcome of the trial (success or failure.}$

```{r}
str(complete_data.Q1)
stat.test.BG <- complete_data.Q1 %>% 
  t_test(basal.ganglia ~ feedback_type) %>%
  add_significance()
stat.test.BG

stat.test.MB <- complete_data.Q1 %>% 
  t_test(midbrain ~ feedback_type) %>%
  add_significance()
stat.test.MB

stat.test.VC <- complete_data.Q1 %>% 
  t_test(vis.ctx ~ feedback_type) %>%
  add_significance()
stat.test.VC

stat.test.OC <- complete_data.Q1 %>% 
  t_test(other.ctx ~ feedback_type) %>%
  add_significance()
stat.test.OC
```

\ \

##### $\bf \text{Boxplots for brain regions vs feedback_type:}$

```{r}


bxp.bg <- ggboxplot(
  complete_data.Q1, x = "feedback_type", y = "basal.ganglia", 
  ylab = "basal.ganglia", xlab = "feedback.type", color=c("red","blue" ), fill = c("wheat","grey")
  )
#bxp.bg

bxp.mb <- ggboxplot(
  complete_data.Q1, x = "feedback_type", y = "midbrain", 
  ylab = "mid.brain", xlab = "feedback.type", color=c("red","blue" ), fill = c("wheat","grey")
  )
#bxp.mb

bxp.vc <- ggboxplot(
  complete_data.Q1, x = "feedback_type", y = "vis.ctx", 
  ylab = "visual.cortex", xlab = "feedback.type", color=c("red","blue" ), fill = c("wheat","grey")
  )
#bxp.vc

bxp.oc <- ggboxplot(
  complete_data.Q1, x = "feedback_type", y = "other.ctx", 
  ylab = "other.cortex", xlab = "feedback.type", color=c("red","blue" ), fill = c("wheat","grey")
  )
#bxp.oc

grid.arrange(bxp.bg,bxp.mb,bxp.vc,bxp.oc, ncol=2)
#par(mfrow = c(2, 2))

```


\ \

##### $\bf \text{Question 2. Build a predictive model to forecast the reaction (-1, 0, or 1) given the neural activity across}$
##### $\bf \text{all regions. Here the neural activity is restricted to the period between 0.2 seconds before stimulus onset,}$
##### $\bf \text{and 0.4 after the stimulus onset or before the reaction.}$

```{r}
str(complete_data.Q2)
```

```{r}
summdata.Q2.b = group_by(complete_data.Q2, trial.no) %>%
  summarise(
    trial.no = as.numeric(trial.no),
    mean_basal.ganglia = mean(basal.ganglia),
    mean_midbrain=mean(midbrain),
    mean_other.ctx=mean(other.ctx), 
    mean_vis.ctx=mean(vis.ctx),
  )
summdata.Q2.b<-data.frame(unique(summdata.Q2.b))
summ_table.Q2.b<-knitr::kable(summdata.Q2.b, caption = "Table: Summary statistics of infection count  by vita and time")

dim(summdata.Q2.b)
```


```{r}
#print(arrange(summdata.Q2.b))
```

```{r}
ndata.Q2.b<-cbind(summdata.Q2.b, as.vector(dat$feedback_type), as.vector(dat$response), as.vector(dat$contrast_left-dat$contrast_right))
names(ndata.Q2.b)<-c("trial.no","mean_basal.ganglia","mean_midbrain","mean_other.ctx","mean_vis.ctx","feedback_type", "response","stimulus_type")
str(ndata.Q2.b)
```


```{r}
table(ndata.Q2.b$response)
```

##### $\bf \text{Dataset-I for Question 2:}$

```{r}
gee.data1<- ndata.Q2.b[!ndata.Q2.b$response == -1, ]

gee.data1$trial.no<-as.factor(gee.data1$trial.no)
gee.data1$feedback_type<-as.factor(gee.data1$feedback_type)
#gee.data1$response<-as.factor(gee.data1$response)
gee.data1$stimulus_type<-as.factor(gee.data1$stimulus_type)

dim(gee.data1)
str(gee.data1)
```

##### $\bf \text{Dataset-II for Question 2:}$

```{r}
gee.data2<- ndata.Q2.b[!ndata.Q2.b$response == 1, ]
gee.data2["response"][gee.data2["response"] == -1] <- 1

gee.data2$trial.no<-as.factor(gee.data2$trial.no)
gee.data2$feedback_type<-as.factor(gee.data2$feedback_type)
#gee.data2$response<-as.factor(gee.data2$response)
gee.data2$stimulus_type<-as.factor(gee.data2$stimulus_type)

dim(gee.data2)
str(gee.data2)
```

##### $\bf \text{Dataset-III for Question 2:}$

```{r}
gee.data3<- ndata.Q2.b[!ndata.Q2.b$response == 0, ]
gee.data3["response"][gee.data3["response"] == -1] <- 0

gee.data3$trial.no<-as.factor(gee.data3$trial.no)
gee.data3$feedback_type<-as.factor(gee.data3$feedback_type)
#gee.data1$response<-as.factor(gee.data1$response)
gee.data3$stimulus_type<-as.factor(gee.data3$stimulus_type)

dim(gee.data3)
str(gee.data3)
```

```{r}
table(gee.data1$response)
table(gee.data2$response)
table(gee.data3$response)
```

##### $\bf \text{Correlation matrix:}$

```{r}
cor(gee.data1[,-c(1,6:8)],use="pairwise.complete.obs")
cor(gee.data2[,-c(1,6:8)],use="pairwise.complete.obs")
cor(gee.data3[,-c(1,6:8)],use="pairwise.complete.obs")
```


```{r}
library(dplyr)
gee.data1<-gee.data1 %>%
  mutate(stimulus_type=recode(stimulus_type, '-1'='-1','-0.75'='-1','-0.5'='-1','-0.25'='-1', '1'='1','0.75'='1','0.5'='1','0.25'='1'))
dim(gee.data1)

#str(gee.data1)
gee.data1$stimulus_type<-relevel(gee.data1$stimulus_type,"0")

gee.model1 <- geeglm(response~mean_basal.ganglia+mean_midbrain+mean_other.ctx+mean_vis.ctx+stimulus_type, data=gee.data1, id = stimulus_type, family=binomial(link="logit"), corstr="ar1")
summary(gee.model1)
```


```{r}
gee.model1int <- geeglm(response~mean_basal.ganglia*stimulus_type+mean_midbrain*stimulus_type+mean_other.ctx*stimulus_type+mean_vis.ctx*stimulus_type, data=gee.data1, id = stimulus_type, family=binomial(link="logit"), corstr="ar1")
summary(gee.model1int)
```

```{r}
gee.data2<-gee.data2 %>%
  mutate(stimulus_type=recode(stimulus_type, '-1'='-1','-0.75'='-1','-0.5'='-1','-0.25'='-1', '1'='1','0.75'='1','0.5'='1','0.25'='1'))
dim(gee.data2)

gee.data2$stimulus_type<-relevel(gee.data2$stimulus_type,"0")

gee.model2 <- geeglm(response~mean_basal.ganglia+mean_midbrain+mean_other.ctx+mean_vis.ctx+stimulus_type, data=gee.data2, id = stimulus_type, family=binomial(link="logit"), corstr="ar1")
summary(gee.model2)
```


```{r}
gee.model2int <- geeglm(response~mean_basal.ganglia*stimulus_type+mean_midbrain*stimulus_type+mean_other.ctx*stimulus_type+mean_vis.ctx*stimulus_type, data=gee.data2, id = stimulus_type, family=binomial(link="logit"), corstr="ar1")
summary(gee.model2int)
```

```{r}
gee.data3<-gee.data3 %>%
  mutate(stimulus_type=recode(stimulus_type, '-1'='-1','-0.75'='-1','-0.5'='-1','-0.25'='-1', '1'='1','0.75'='1','0.5'='1','0.25'='1'))
dim(gee.data3)

gee.data3$stimulus_type<-relevel(gee.data3$stimulus_type,"0")

gee.model3 <- geeglm(response~mean_basal.ganglia+mean_midbrain+mean_other.ctx+mean_vis.ctx+stimulus_type, data=gee.data3, id = stimulus_type, family=binomial(link="logit"), corstr="ar1")
summary(gee.model3)
```


```{r}
gee.model3int <- geeglm(response~mean_basal.ganglia*stimulus_type+mean_midbrain*stimulus_type+mean_other.ctx*stimulus_type+mean_vis.ctx*stimulus_type, data=gee.data3, id = stimulus_type, family=binomial(link="logit"), corstr="ar1")
summary(gee.model3int)
```


```{r}

```


##### $\bf \text{Boxplots:}$

```{r}
bpBG1<-ggplot(gee.data1, aes(x=stimulus_type, y= mean_basal.ganglia, fill=stimulus_type)) + 
    geom_boxplot()+
    labs(y = "mean Basal Ganglia")+
   scale_fill_discrete(labels = c("0: neutral", "-1: negative", "1: positive"))+
  theme_classic()

#### Distribution of cdiox: boxplot
bpMB1<-ggplot(gee.data1, aes(x=stimulus_type, y= mean_midbrain, fill=stimulus_type)) + 
    geom_boxplot()+
    labs(y = "mean Midbrain")+
  scale_fill_discrete(labels = c("0: neutral", "-1: negative", "1: positive"))+
  theme_classic()

bpVC1<-ggplot(gee.data1, aes(x=stimulus_type, y= mean_vis.ctx, fill=stimulus_type)) + 
    geom_boxplot()+
    labs (y = "mean Visual Cortex")+
  scale_fill_discrete(labels = c("0: neutral", "-1: negative", "1: positive"))+
  theme_classic()

bpOC1<-ggplot(gee.data1, aes(x=stimulus_type, y= mean_other.ctx, fill=stimulus_type)) + 
    geom_boxplot()+
    labs(y = "mean other Cortex")+
  scale_fill_discrete(labels = c("0: neutral", "-1: negative", "1: positive"))+
  theme_classic()
grid.arrange(bpBG1,bpMB1,bpVC1,bpOC1)

bpBG2<-ggplot(gee.data2, aes(x=stimulus_type, y= mean_basal.ganglia, fill=stimulus_type)) + 
    geom_boxplot()+
    labs(y = "mean Basal Ganglia")+
  scale_fill_discrete(labels = c("0: neutral", "-1: negative", "1: positive"))+
  theme_classic()

#### Distribution of cdiox: boxplot
bpMB2<-ggplot(gee.data2, aes(x=stimulus_type, y= mean_midbrain, fill=stimulus_type)) + 
    geom_boxplot()+
    labs(y = "mean Midbrain")+
  scale_fill_discrete(labels = c("0: neutral", "-1: negative", "1: positive"))+
  theme_classic()

bpVC2<-ggplot(gee.data2, aes(x=stimulus_type, y= mean_vis.ctx, fill=stimulus_type)) + 
    geom_boxplot()+
    labs(y = "mean Visual Cortex")+
  scale_fill_discrete(labels = c("0: neutral", "-1: negative", "1: positive"))+
  theme_classic()

bpOC2<-ggplot(gee.data2, aes(x=stimulus_type, y= mean_other.ctx, fill=stimulus_type)) + 
    geom_boxplot()+
    labs(y = "mean other Cortex")+
  scale_fill_discrete(labels = c("0: neutral", "-1: negative", "1: positive"))+
  theme_classic()
grid.arrange(bpBG2,bpMB2,bpVC2,bpOC2)

bpBG3<-ggplot(gee.data3, aes(x=stimulus_type, y= mean_basal.ganglia, fill=stimulus_type)) + 
    geom_boxplot()+
    labs(y = "mean Basal Ganglia")+
  scale_fill_discrete(labels = c("0: neutral", "-1: negative", "1: positive"))+
  theme_classic()

#### Distribution of cdiox: boxplot
bpMB3<-ggplot(gee.data3, aes(x=stimulus_type, y= mean_midbrain, fill=stimulus_type)) + 
    geom_boxplot()+
    labs(y = "mean Midbrain")+
  scale_fill_discrete(labels = c("0: neutral", "-1: negative", "1: positive"))+
  theme_classic()

bpVC3<-ggplot(gee.data3, aes(x=stimulus_type, y= mean_vis.ctx, fill=stimulus_type)) + 
    geom_boxplot()+
    labs( y = "mean Visual Cortex")+
  scale_fill_discrete(labels = c("0: neutral", "-1: negative", "1: positive"))+
  theme_classic()

bpOC3<-ggplot(gee.data3, aes(x=stimulus_type, y= mean_other.ctx, fill=stimulus_type)) + 
    geom_boxplot()+
    labs(y = "mean other Cortex")+
  scale_fill_discrete(labels = c("0: neutral", "-1: negative", "1: positive"))+
  theme_classic()
grid.arrange(bpBG3,bpMB3,bpVC3,bpOC3)
```


```{r}
coef(gee.model1)
vcov(gee.model1)
summary(gee.model1)
coef(summary(gee.model1))
```


##### $\bf \text{Models with smaller values of QIC, CIC, QICu, or QICC are preferred}$

##### $\bf \text{Comparison between model}$

```{r}
QIC(gee.model1)
QIC(gee.model1int)

QIC(gee.model2)
QIC(gee.model2int)

QIC(gee.model3)
QIC(gee.model3int)

```

```{r}
anova(gee.model1,gee.model1int)
anova(gee.model2,gee.model2int)
anova(gee.model3,gee.model3int)
```
